RJObject Paper

### 2014-06-21 Documents/Paper/ms.tex
Subsections for the different proposals
Removed braces

\section{Metropolis proposals for the general problem}
We will now define a set of proposal distributions that could be used to
sample the prior distribution
$p(N, \alpha, \{x_i\}) = p(N) p(\alpha) \prod_{i=1}^N p(\{x_i\} | \alpha)$.
These proposals will need to satisfy detailed balance in order to be valid
when used inside DNS. The proposals will also be very heavy tailed. When
DNS is exploring a distribution close to the prior, large proposals will
generally be needed. When DNS is exploring a distribution constrained to
very high values of the likelihood function, much smaller proposals will be
appropriate. Rather than attempting expensive tuning (since the number of
distributions involved may number in the hundreds or even thousands), we will
apply the heavy tailed proposal distributions and simply accept that there will
be some waste.

@@

>>>>

% Consider terminology: "objects" vs. "components"

\section{Metropolis proposals for the general problem}
We will now define a set of proposal distributions that could be used to
sample the prior distribution
$p(N, \alpha, \{x_i\}) = p(N) p(\alpha) \prod_{i=1}^N p(x_i | \alpha)$.
These proposals will need to satisfy detailed balance in order to be valid
when used inside DNS. The proposals will also be very heavy tailed. When
DNS is exploring a distribution close to the prior, large proposals will
generally be needed. When DNS is exploring a distribution constrained to
very high values of the likelihood function, much smaller proposals will be
appropriate. Rather than attempting expensive tuning (since the number of
distributions involved may number in the hundreds or even thousands), we will
apply the heavy tailed proposal distributions and simply accept that there will
be some waste.

@@

\subsection{Proposals that modify objects}

\subsection{Proposals that change the hyperparameters, keeping the objects fixed}

\subsection{Proposals that change the hyperparameters and all of the objects}
